The Aquarius Stream Progenitor Was Not A Globular Cluster: \\ Its History Could Be Far More Interesting\altaffilmark{1}

### 2012-12-28 2012-aqs/draft-aqs.tex
Added equivalent widths table and some discussion text

Wide-field surveys have proved excellent sources for finding galactic substructures, including stellar streams. Dozens of streams reaching out up to 150\,kpc in the halo have been identified through photometric selections and matched-filtering techniques \citep{Belokurov;et-al_2007;Koposov_SG1}. However, as \citet{Helmi;White_1999} point out, these approaches are only successful for identifying substructures that are sufficiently distant from the solar neighbourhood. A nearby stream within $\sim{}$10\,kpc will not appear as an on-sky over-density, as the stars would be sparsely positioned across the sky. Such substructures would only be detectable with kinematic, or perhaps precise chemical information.

@@

% QUANTIFYING THE STREAM DETECTION
Upon examining the galactic longitude and radial velocities of Aquarius stars, the stream appears quite distinct from the halo. In order to quantify the statistical likelihood that the Aquarius stream is a true substructure, \citet{WIlliams;et-al_2011} compared the number of observed RAVE stars within $-70\,^\circ < b < -50\,^\circ$ against the Galaxia \citep{Sharma;et-al_2009} and Besan\c{c}on \citep{Robin;et-al_2003} galaxy models. Predicted particles and observed stars between $-70\,^\circ < b < -50\,^\circ$ were binned in $\Delta{l} \times \Delta{V_{hel}}$ using varying grid cell sizes between $25-70\,^\circ$ and 20-100\,km s$^{-1}$ respectively. The significance of the stream is calculated for each cell. \citet{williams;et-al_2011} found the stream to be statistically significant ($>$4-$\sigma$) in 96\% of the grid cell sizes employed for the Besan\c{c}on model. By sampling the Galaxia model multiple times with varying extinction models, a similar result was found: between $75\pm15$\,\% to $80\pm18$\,\% of grid cells showed the Aquarius stream to significant at the 4-$\sigma$ level. Given the high-latitude of the stream and proximity of the stream, it is not surprising that dust had a negligible effect on the overall significance. \citet{williams;et-al_2011} concluded that the over-density in $l, V_{hel}$ is a true substructure, and neither the choice of galaxy model, cell size, nor the extinction model made any real difference to the stream detection significance.

@@

There are other abundances patterns that allow us to infer the chemical evolution of a given cluster. \citet{Nissen;Schuster_1997} first noted that only the distant solar neighbourhood stars were enriched in [Ni/Fe] and [Na/Fe]. \citet{fulbright;et-al_2000} came to a similar conclusion: only somewhat distant ($R_\odot > 20$\,kpc) stars are likely to be sodium deficient. If the stellar halo has been built up from the accretion of smaller dwarf satellites, \citet{Nissen;Schuster_1997} proposed that this chemical trend may be indicative of the halo merger history. Although there are some caveats to this chemical pattern (see \S\ref{sec:ni-na-relation}), at the very least the Na-Ni correlation may provide an indication whether stars became chemically enriched in dSph-like environments. \citet{wylie-de-boer;et-al_2012} found all their Aquarius stars to be enriched in both sodium and nickel; contrary to what would be expected if the stars originated from a disrupted dSph satellite.

@@

We seek to investigate the nature of the Aquarius stream, in particular the recent globular cluster origin claim made by \citet{wylie-de-boer;et-al_2012}. We present a detailed analysis for five confirmed Aquarius stream members from high-resolution, high S/N observations taken using the Magellan Inamori Kyocera Echelle spectrograph \citep{Bernstein;et-al_2003} on the Magellan Clay telescope. Our analysis includes determining the galactic dynamics and orbital paths for the Aquarius stream, and measuring precise chemical abundances. Details of the observations and data reduction are outlined in the following section. The data analysis is chronicalled in \S\ref{sec:analysis} and a detailed discussion of these results resides in \S\ref{sec:discussion}. In \S\ref{sec:conclusion} we present our conclusions and critical interpretations.

@@

Calibration frames were taken at the start of each night, including twenty flat-field frames (10 quartz, 10 milky) and 10 Th-Ar arc lamp exposures for wavelength calibration. The data were reduced using the CarPy pipeline\footnote{carpy website url}. One of our standard stars, HD 41667, was also reduced using standard extraction and calibration methods in \textsc{IRAF}. The resultant spectra from both reduction workflows were compared for residual fringing, S/N, and wavelength calibration. No noteworthy differences were present, and the CarPy pipeline was utilized for the remainder of our reductions. Each reduced echelle order was carefully normalised using a third order spline. Normalised orders  for a given star were stitched together to provide a single one-dimensional spectrum from 3800-9400\,\AA{}.

@@

For the measurement of atomic absorption lines, we employed the line list of \citet{yong;et-al_2005} with additional transitions of Cr, Sc, Zn, and Sr from \citet{frebel;et-al_2010}. We supplemented the list with hyperfine-structure data for Sc and Mn from the Kurucz compilation \citet{Kurucz;1998}. Molecular line data for CH was taken from \citet{Plez;et-al_2008,Plez;et-al_2009}. For lines with hyperfine structure, blended transitions or molecular features, we determined the transition abundance using a spectral synthesis approach where the abundance of a given species is found by by matching a synthetic spectrum to the observed spectrum. Equivalent widths were measured to determine the abundances of all other transitions.

@@

We note that the results of our iterative fitting approach are \textit{completely insensitive} to the initial FWHM guess. Increasing the initial FWHM estimate from 0.1\,\AA{} to 1 or 2\,\AA{} -- unphysically large values for high-resolution spectra -- does not alter \textit{any} of our final equivalent width (or FWHM) measurements. Only a small increase in computational cost is observed. Although we are extremely confident in our automatic equivalent width measurements, every absorption profile was examined by eye for quality, and spurious measurements were excluded.

We list the atomic data and measured equivalent widths for atomic lines used during this analysis in Table \ref{tab:equivalent-widths}. Saturated lines were excluded by removing measurements with reduced equivalent widths, $\log_{10}{(EW/\lambda)} > -4.5$\, dex. A minimum detectable equivalent width was calculated as a function of wavelength based on the S/N, and only lines that exceeded a $3\sigma$ detection significance were included. We have verified our equivalent width measurement techniques by comparing our measurements for 164 lines in HD140283 with the study of \citet{norris;et-al_1996}. Excellent agreement is found between the two studies, which is illustrated in Figure \ref{fig:ew-compare}. The mean difference between this study and that of \cite{norris;et-al_1996} is a negligible $0.64 \pm 2.78$\,m\AA{}, and no systematic trend is present.

% need to mention that we only used the "Good" Norris measurements

% equivalent widths plot with Norris for HD 122563
\begin{figure}[h]
	\includegraphics[width=\columnwidth]{./figures/smh-norris.pdf}
	\caption{A comparison showing equivalent widths measured for HD140283 using our automatic routine (see \S\ref{sec:line-measurements}), and those found with careful hand measurements by \citet{norris;et-al_1996}. No systematic trend is present, and the mean difference between these studies is $\langle\Delta{}W_\lambda\rangle = -0.64 \pm 2.78$ m\AA{}.}
	\label{fig:ew-compare}
\end{figure}

>>>>

Wide-field surveys have proved excellent sources for finding galactic substructures, including stellar streams. Dozens of streams reaching out up to 150\,kpc in the halo have been identified through photometric selections and matched-filtering techniques \citep{belokurov;et-al_2007,koposov_SG1}. However, as \citet{helmi;white_1999} point out, these approaches are only successful for identifying substructures that are sufficiently distant from the solar neighbourhood. A nearby stream within $\sim{}$10\,kpc will not appear as an on-sky over-density, as the stars would be sparsely positioned across the sky. Such substructures would only be detectable with kinematic, or perhaps precise chemical information.

@@

% QUANTIFYING THE STREAM DETECTION
Upon examining the galactic longitude and radial velocities of Aquarius stars, the stream appears quite distinct from the halo. In order to quantify the statistical likelihood that the Aquarius stream is a true substructure, \citet{williams;et-al_2011} compared the number of observed RAVE stars within $-70\,^\circ < b < -50\,^\circ$ against the Galaxia \citep{sharma;et-al_2011} and Besan\c{c}on \citep{robin;et-al_2003} galaxy models. Predicted particles and observed stars between $-70\,^\circ < b < -50\,^\circ$ were binned in $\Delta{l} \times \Delta{V_{hel}}$ using varying grid cell sizes between $25-70\,^\circ$ and 20-100\,km s$^{-1}$ respectively. The significance of the stream is calculated for each cell. \citet{williams;et-al_2011} found the stream to be statistically significant ($>$4-$\sigma$) in 96\% of the grid cell sizes employed for the Besan\c{c}on model. By sampling the Galaxia model multiple times with varying extinction models, a similar result was found: between $75\pm15$\,\% to $80\pm18$\,\% of grid cells showed the Aquarius stream to significant at the 4-$\sigma$ level. Given the high-latitude of the stream and proximity of the stream, it is not surprising that dust had a negligible effect on the overall significance. \citet{williams;et-al_2011} concluded that the over-density in $l, V_{hel}$ is a true substructure, and neither the choice of galaxy model, cell size, nor the extinction model made any real difference to the stream detection significance.

@@

There are other abundances patterns that allow us to infer the chemical evolution of a given cluster. \citet{nissen;schuster_1997} first noted that only the distant solar neighbourhood stars were enriched in [Ni/Fe] and [Na/Fe]. \citet{fulbright_2000} came to a similar conclusion: only somewhat distant ($R_\odot > 20$\,kpc) stars are likely to be sodium deficient. If the stellar halo has been built up from the accretion of smaller dwarf satellites, \citet{nissen;schuster_1997} proposed that this chemical trend may be indicative of the halo merger history. Although there are some caveats to this chemical pattern (see \S\ref{sec:ni-na-relation}), at the very least the Na-Ni correlation may provide an indication whether stars became chemically enriched in dSph-like environments. \citet{wylie-de-boer;et-al_2012} found all their Aquarius stars to be enriched in both sodium and nickel; contrary to what would be expected if the stars originated from a disrupted dSph satellite.

@@

We seek to investigate the nature of the Aquarius stream, in particular the recent globular cluster origin claim made by \citet{wylie-de-boer;et-al_2012}. We present a detailed analysis for five confirmed Aquarius stream members from high-resolution, high S/N observations taken using the Magellan Inamori Kyocera Echelle spectrograph \citep{bernstein;et-al_2003} on the Magellan Clay telescope. Our analysis includes determining the galactic dynamics and orbital paths for the Aquarius stream, and measuring precise chemical abundances. Details of the observations and data reduction are outlined in the following section. The data analysis is chronicalled in \S\ref{sec:analysis} and a detailed discussion of these results resides in \S\ref{sec:discussion}. In \S\ref{sec:conclusion} we present our conclusions and critical interpretations.

@@

% what spectral resolution in the blue, what resolution in the red

Calibration frames were taken at the start of each night, including twenty flat-field frames (10 quartz, 10 milky) and 10 Th-Ar arc lamp exposures for wavelength calibration. The data were reduced using the CarPy pipeline\footnote{http://code.obs.carnegiescience.edu/mike}. One of our standard stars, HD 41667, was also reduced using standard extraction and calibration methods in \textsc{iraf}. The resultant spectra from both reduction workflows were compared for residual fringing, S/N, and wavelength calibration. No noteworthy differences were present, and the CarPy pipeline was utilized for the remainder of our reductions. Each reduced echelle order was carefully normalised using a third order spline. Normalised orders  for a given star were stitched together to provide a single one-dimensional spectrum from 3800-9400\,\AA{}.

@@

For the measurement of atomic absorption lines, we employed the line list of \citet{yong;et-al_2005} with additional transitions of Cr, Sc, Zn, and Sr from \citet{frebel;et-al_2010}. We supplemented the list with hyperfine-structure data for Sc and Mn from the Kurucz compilation \citet{kurucz;1998}. Molecular line data for CH was taken from \citet{plez;et-al_2008,plez;et-al_2009}. For lines with hyperfine structure, blended transitions or molecular features, we determined the transition abundance using a spectral synthesis approach where the abundance of a given species is found by by matching a synthetic spectrum to the observed spectrum. Equivalent widths were measured to determine the abundances of all other transitions.

@@

The results of our iterative fitting approach are completely \textit{insensitive} to the initial FWHM guess. Increasing the initial FWHM estimate from 0.1\,\AA{} to 1 or 2\,\AA{} -- unphysically large values for high-resolution spectra -- does not alter either the FWHM or the equivalent width for any of our measurements. Only a small increase in computational cost is observed. Although we are extremely confident in our automatic equivalent width measurements, every absorption profile was examined by eye for quality, and spurious measurements were excluded.

We list the atomic data and measured equivalent widths for atomic lines used during this analysis in Table \ref{tab:equivalent-widths}. Saturated lines were excluded by removing measurements with reduced equivalent widths, $\log_{10}{(EW/\lambda)} > -4.5$\, dex. A minimum detectable equivalent width was calculated as a function of wavelength based on the S/N, and only lines that exceeded a $3\sigma$ detection significance were included. We have verified our equivalent width measurement techniques by comparing our measurements for 156 lines in HD140283 with the study of \citet{norris;et-al_1996}. We only included measurements in the \citet{norris;et-al_1996} study that were not marked with line quality parameters. Excellent agreement is found between the two studies, which is illustrated in Figure \ref{fig:ew-compare}. The mean difference between this study and that of \cite{norris;et-al_1996} is a negligible $0.64 \pm 2.78$\,m\AA{}, and no systematic trend is present. We note that the scatter in measurement differences is likely to be directly attributed to the observed $S/N$, as other studies using the same EW measurement software described here find better agreement with hand measurements for spectra with higher $S/N$ ($0.20 \pm 0.16$\,m{\AA} with $S/N \sim X$, $0.25 \pm 0.28$\,m{\AA} with $S/N \sim{} Y$; \citet{frebel;et-al_2013}).

% equivalent widths plot with Norris for HD 122563
\begin{figure}[h]
	\includegraphics[width=\columnwidth]{./figures/smh-norris.pdf}
	\caption{A comparison showing equivalent widths measured for HD 140283 using our automatic routine (see \S\ref{sec:line-measurements}), and those found by careful hand measurements in \citet{norris;et-al_1996}. No systematic trend is present, and the mean difference between these studies is $\langle\Delta{}W_\lambda\rangle = -0.64 \pm 2.78$ m\AA{}.}
	\label{fig:ew-compare}
\end{figure}

\begin{deluxetable*}{cccccccccc}
\tablecolumns{1}
\tabletypesize{\scriptsize}
\tablecaption{List of Line Transitions and Equivalent Width Measurements}
	& & & & \multicolumn{5}{c}{Equivalent Width} \\
	\cline{5-9} \\
	\colhead{Wavelength} &
	\colhead{Transition} &
	\colhead{LEP} &
	\colhead{$\log{gf}$} &
	\colhead{C2225316-14437} &
	\colhead{C2306265-085103} &
	\colhead{J221821-183424} &
	\colhead{J223504-152834} &
	\colhead{J223811-104126} \\
	({\AA})	& & (eV) & & (m{\AA}) & (m{\AA}) & (m{\AA}) & (m{\AA}) & (m{\AA}) 
 6300.300 &       8.0 &      0.00 &    --9.717 &     45.37 &     66.93 &     38.48 &     32.85 &     17.87 \\
 6363.780 &       8.0 &      0.02 &   --10.185 &     19.47 &     28.31 &     12.96 &     18.83 &   \nodata \\
 5688.190 &      11.0 &      2.11 &    --0.420 &   \nodata &   \nodata &     48.97 &    131.49 &     38.41 \\
 6154.230 &      11.0 &      2.10 &    --1.530 &     24.06 &     38.89 &   \nodata &     48.49 &   \nodata \\
 6160.750 &      11.0 &      2.10 &    --1.230 &     37.72 &     58.49 &   \nodata &     65.72 &   \nodata \\
 6318.720 &      12.0 &      5.11 &    --1.970 &   \nodata &     47.94 &     14.69 &     62.79 &      8.88 \\
 6319.240 &      12.0 &      5.11 &    --2.220 &     30.84 &   \nodata &      5.51 &   \nodata &   \nodata \\
 6965.410 &      12.0 &      5.75 &    --1.510 &   \nodata &   \nodata &   \nodata &     59.22 &   \nodata \\
 7387.690 &      12.0 &      5.75 &    --0.870 &     51.71 &     56.30 &     24.68 &     76.01 &     23.99 \\
 6696.020 &      13.0 &      3.14 &    --1.340 &     72.83 &     63.60 &     12.99 &   \nodata &   \nodata \\
 6698.670 &      13.0 &      3.14 &    --1.640 &     39.67 &     33.44 &   \nodata &     39.50 &   \nodata \\
 7835.310 &      13.0 &      4.02 &    --0.470 &     47.77 &     38.44 &   \nodata &     55.91 &      5.39 \\
 7836.130 &      13.0 &      4.02 &    --0.310 &     62.78 &     44.72 &   \nodata &     69.13 &     13.23 \\
 5690.430 &      14.0 &      4.93 &    --1.751 &     56.17 &     43.76 &     25.75 &     53.45 &     16.77 \\
 5793.070 &      14.0 &      4.93 &    --1.843 &     46.13 &     39.81 &     19.33 &     48.39 &   \nodata \\
 6125.020 &      14.0 &      5.61 &    --1.506 &     40.93 &     23.45 &     10.86 &     34.74 &   \nodata \\
 6145.010 &      14.0 &      5.62 &    --1.362 &     33.93 &     21.66 &     16.11 &     32.75 &     10.02 \\
 6155.130 &      14.0 &      5.62 &    --0.786 &     67.36 &     53.11 &     35.29 &     72.00 &     24.98 \\
 6166.440 &      20.0 &      2.52 &    --1.142 &     94.19 &    105.46 &     42.32 &     99.45 &     35.88 \\
 6169.040 &      20.0 &      2.52 &    --0.797 &    112.06 &    120.91 &     66.31 &    120.48 &     55.48 \\
 6169.560 &      20.0 &      2.53 &    --0.478 &    127.89 &    141.16 &     83.69 &    136.37 &     71.35 \\
 6455.600 &      20.0 &      2.52 &    --1.290 &     80.79 &     91.41 &     31.35 &     89.20 &     25.98 \\
 5526.820 &      21.1 &      1.77 &      0.130 &     98.84 &    113.34 &    100.84 &     98.40 &     51.08 \\
 5657.880 &      21.1 &      1.51 &    --0.500 &     96.46 &    107.49 &     92.74 &     95.42 &     41.21 \\
 5667.150 &      21.1 &      1.50 &    --1.240 &     59.41 &     75.04 &     45.00 &     58.54 &     14.51 \\
 5669.040 &      21.1 &      1.50 &    --1.120 &   \nodata &     92.51 &     57.27 &     75.19 &     18.20 \\
 6245.610 &      21.1 &      1.51 &    --0.980 &     67.12 &     83.60 &     53.34 &     67.38 &     14.75 \\
 6604.600 &      21.1 &      1.36 &    --1.480 &     65.58 &     82.06 &     49.37 &     65.92 &     17.81 \\
 6064.630 &      22.0 &      1.05 &    --1.888 &     59.69 &     80.86 &   \nodata &     58.58 &   \nodata \\
 6091.170 &      22.0 &      2.27 &    --0.367 &     45.15 &     59.09 &   \nodata &     56.28 &   \nodata \\
 6312.240 &      22.0 &      1.46 &    --1.496 &     46.16 &     63.41 &   \nodata &     48.78 &   \nodata \\
 6336.100 &      22.0 &      1.44 &    --1.687 &     35.88 &     54.10 &   \nodata &     42.33 &   \nodata \\
 5154.080 &      22.1 &      1.57 &    --1.920 &    112.25 &   \nodata &    114.05 &   \nodata &     53.89 \\
 5185.910 &      22.1 &      1.89 &    --1.350 &   \nodata &    101.45 &    105.46 &   \nodata &     55.30 \\
 5336.790 &      22.1 &      1.58 &    --1.690 &    116.30 &    124.58 &    119.55 &    103.98 &     61.40 \\
 5381.030 &      22.1 &      1.59 &    --2.080 &   \nodata &    131.44 &    101.94 &    109.93 &     47.96 \\
 5727.060 &      23.0 &      1.08 &    --0.010 &    122.36 &   \nodata &     26.00 &    116.79 &      9.13 \\
 6090.220 &      23.0 &      1.08 &    --0.060 &     93.58 &    115.58 &     23.62 &     92.84 &   \nodata \\
 6216.360 &      23.0 &      0.28 &    --1.290 &    108.80 &   \nodata &     16.92 &    109.33 &   \nodata \\
 6251.820 &      23.0 &      0.29 &    --1.340 &     94.66 &    124.37 &   \nodata &     92.43 &   \nodata \\
 6274.640 &      23.0 &      0.27 &    --1.670 &     65.49 &     93.82 &   \nodata &     61.51 &   \nodata \\
 6504.160 &      23.0 &      1.18 &    --1.230 &     22.95 &     33.69 &   \nodata &     31.93 &   \nodata \\
 4545.950 &      24.0 &      0.94 &    --1.370 &   \nodata &   \nodata &     80.22 &   \nodata &   \nodata \\
 4580.056 &      24.0 &      0.94 &    --1.650 &   \nodata &   \nodata &   \nodata &   \nodata &     44.22 \\
 4616.137 &      24.0 &      0.98 &    --1.190 &    128.75 &    139.25 &     89.37 &    126.24 &     59.88 \\
 4626.188 &      24.0 &      0.97 &    --1.320 &    122.24 &    136.41 &     82.24 &   \nodata &     56.90 \\
 4646.150 &      24.0 &      1.03 &    --0.740 &   \nodata &   \nodata &    110.65 &    146.08 &     75.35 \\
 4651.280 &      24.0 &      0.98 &    --1.460 &    127.78 &    140.58 &     75.40 &    116.31 &     48.44 \\
 4652.158 &      24.0 &      1.00 &    --1.030 &    138.48 &   \nodata &     96.92 &    138.00 &     66.74 \\
 5206.040 &      24.0 &      0.94 &      0.020 &   \nodata &   \nodata &   \nodata &   \nodata &    132.81 \\
 5247.564 &      24.0 &      0.96 &    --1.640 &    141.39 &   \nodata &     76.09 &   \nodata &     46.66 \\
 5296.690 &      24.0 &      0.98 &    --1.360 &    149.87 &   \nodata &     85.01 &    140.97 &     59.00 \\
 5300.740 &      24.0 &      0.98 &    --2.000 &    120.48 &   \nodata &   \nodata &    112.22 &   \nodata \\
 5345.800 &      24.0 &      1.00 &    --0.950 &   \nodata &   \nodata &    115.38 &   \nodata &     81.14 \\
 5348.310 &      24.0 &      1.00 &    --1.210 &    150.80 &   \nodata &     94.76 &    142.37 &     63.02 \\
 5409.770 &      24.0 &      1.03 &    --0.670 &   \nodata &   \nodata &    132.36 &   \nodata &     92.13 \\
 4558.594 &      24.1 &      4.07 &    --0.656 &   \nodata &   \nodata &   \nodata &    101.77 &     46.52 \\
 4588.142 &      24.1 &      4.07 &    --0.826 &     46.04 &     52.99 &     60.53 &     55.00 &     35.95 \\
 4591.992 &      24.1 &      4.07 &    --1.419 &   \nodata &   \nodata &     29.08 &     28.53 &     19.56 \\
 6013.530 &      25.0 &      3.07 &    --0.251 &     89.19 &    114.55 &     22.18 &    109.41 &     14.81 \\
 6016.670 &      25.0 &      3.08 &    --0.100 &     93.98 &    116.01 &     28.15 &    113.02 &     17.06 \\
 6021.800 &      25.0 &      3.08 &      0.034 &     97.50 &    116.02 &     39.08 &    110.74 &     19.90 \\
 5044.210 &      26.0 &      2.85 &    --2.034 &   \nodata &   \nodata &   \nodata &   \nodata &     33.70 \\
 5054.640 &      26.0 &      3.64 &    --1.938 &     37.96 &   \nodata &   \nodata &   \nodata &   \nodata \\
 5242.490 &      26.0 &      3.63 &    --0.980 &     94.34 &    101.83 &     72.92 &   \nodata &     49.25 \\
 5321.110 &      26.0 &      4.43 &    --1.106 &     34.97 &     35.32 &     11.14 &   \nodata &   \nodata \\
 5322.040 &      26.0 &      2.28 &    --2.840 &     93.10 &    103.03 &     59.48 &   \nodata &     30.88 \\
 5326.140 &      26.0 &      3.57 &    --2.130 &     40.39 &     51.67 &     13.75 &     48.44 &   \nodata \\
 5365.400 &      26.0 &      3.57 &    --1.040 &   \nodata &    100.31 &   \nodata &     93.75 &   \nodata \\
 5367.480 &      26.0 &      4.41 &      0.430 &    108.42 &    118.03 &     92.35 &    119.08 &     73.73 \\
 5379.570 &      26.0 &      3.69 &    --1.530 &     71.36 &     81.40 &     34.91 &     75.65 &     19.57 \\
 5491.840 &      26.0 &      4.18 &    --2.250 &   \nodata &   \nodata &   \nodata &     17.29 &   \nodata \\
 5618.630 &      26.0 &      4.21 &    --1.292 &     43.46 &     54.27 &     20.25 &     57.44 &     11.30 \\
 5701.550 &      26.0 &      2.56 &    --2.216 &    118.51 &    134.78 &     91.77 &    119.47 &     49.50 \\
 5705.470 &      26.0 &      4.30 &    --1.420 &     29.24 &     41.47 &     10.92 &     44.49 &      7.70 \\
 5741.850 &      26.0 &      4.25 &    --1.689 &     36.19 &     37.02 &     13.01 &     48.22 &   \nodata \\
 5775.080 &      26.0 &      4.22 &    --1.310 &     54.96 &     62.12 &     25.34 &     67.38 &     14.67 \\
 5778.450 &      26.0 &      2.59 &    --3.480 &     42.75 &     55.83 &     13.43 &     50.14 &   \nodata \\
 5811.920 &      26.0 &      4.14 &    --2.430 &   \nodata &   \nodata &   \nodata &     10.88 &   \nodata \\
 5837.700 &      26.0 &      4.29 &    --2.340 &   \nodata &   \nodata &   \nodata &     12.94 &   \nodata \\
 5853.160 &      26.0 &      1.49 &    --5.280 &     30.38 &     43.35 &      6.28 &     34.65 &   \nodata \\
 5855.090 &      26.0 &      4.60 &    --1.547 &     13.31 &     20.31 &   \nodata &     22.77 &   \nodata \\
 5856.100 &      26.0 &      4.29 &    --1.640 &     27.88 &     40.19 &   \nodata &     42.69 &   \nodata \\
 5858.790 &      26.0 &      4.22 &    --2.260 &   \nodata &     11.37 &   \nodata &     16.85 &   \nodata \\
 5909.970 &      26.0 &      3.21 &    --2.640 &     55.96 &     72.65 &     18.47 &     63.29 &   \nodata \\
 5916.250 &      26.0 &      2.45 &    --2.994 &     92.92 &    105.08 &     51.17 &     95.37 &     17.67 \\
 5927.800 &      26.0 &      4.65 &    --1.090 &     32.37 &     36.72 &     12.16 &     50.92 &   \nodata \\
 5956.690 &      26.0 &      0.86 &    --4.608 &    121.68 &    143.78 &     70.27 &    107.81 &     25.53 \\
 6012.210 &      26.0 &      2.22 &    --4.070 &     44.36 &     58.79 &     11.51 &     52.96 &   \nodata \\
 6019.360 &      26.0 &      3.57 &    --3.360 &      7.00 &   \nodata &   \nodata &     11.34 &   \nodata \\
 6027.050 &      26.0 &      4.07 &    --1.106 &     66.25 &     77.00 &     36.21 &     77.20 &     23.52 \\
 6054.080 &      26.0 &      4.37 &    --2.310 &      5.63 &      8.08 &   \nodata &     12.92 &   \nodata \\
 6105.130 &      26.0 &      4.55 &    --2.050 &   \nodata &     10.92 &   \nodata &     14.84 &   \nodata \\
 6120.240 &      26.0 &      0.91 &    --5.970 &     35.22 &     52.71 &      8.54 &     32.41 &   \nodata \\
 6151.620 &      26.0 &      2.17 &    --3.299 &     88.90 &    102.90 &     46.94 &     87.04 &     18.19 \\
 6157.730 &      26.0 &      4.08 &    --1.320 &   \nodata &     81.19 &     33.20 &     78.14 &     18.79 \\
 6159.380 &      26.0 &      4.61 &    --1.970 &   \nodata &      9.61 &   \nodata &     13.56 &   \nodata \\
 6165.360 &      26.0 &      4.14 &    --1.490 &     40.57 &     51.56 &     14.17 &     54.02 &     10.84 \\
 6173.340 &      26.0 &      2.22 &    --2.880 &    109.59 &    125.61 &     70.72 &    105.59 &     34.86 \\
 6180.200 &      26.0 &      2.73 &    --2.637 &     86.21 &    100.58 &     44.33 &     91.55 &     20.83 \\
 6200.310 &      26.0 &      2.61 &    --2.437 &    105.22 &    122.16 &     70.78 &    105.43 &     36.60 \\
 6219.280 &      26.0 &      2.20 &    --2.433 &    134.35 &    153.29 &    103.28 &    127.37 &     56.70 \\
 6229.230 &      26.0 &      2.84 &    --2.846 &     60.14 &     73.08 &     21.02 &     65.77 &     13.61 \\
 6232.640 &      26.0 &      3.65 &    --1.283 &     92.59 &    104.33 &     58.26 &    103.00 &     35.63 \\
 6246.320 &      26.0 &      3.60 &    --0.894 &    114.00 &    129.15 &     90.50 &    124.05 &     61.68 \\
 6265.130 &      26.0 &      2.17 &    --2.550 &    132.93 &    154.97 &     94.79 &    129.65 &     55.50 \\
 6270.220 &      26.0 &      2.86 &    --2.500 &     76.71 &     93.59 &     41.22 &     79.05 &     17.41 \\
 6271.280 &      26.0 &      3.33 &    --2.728 &     31.57 &     44.87 &     13.35 &     43.63 &   \nodata \\
 6297.790 &      26.0 &      2.22 &    --2.740 &    119.28 &   \nodata &     81.27 &    111.34 &     42.26 \\
 6301.500 &      26.0 &      3.65 &    --0.766 &    115.00 &    130.57 &     91.09 &    117.86 &   \nodata \\
 6322.690 &      26.0 &      2.59 &    --2.426 &    111.05 &    124.39 &     74.19 &    103.53 &     41.61 \\
 6336.820 &      26.0 &      3.68 &    --0.916 &    106.61 &    116.77 &     81.17 &    113.62 &     52.77 \\
 6353.840 &      26.0 &      0.91 &    --6.477 &     11.78 &     23.73 &   \nodata &     14.12 &   \nodata \\
 6355.030 &      26.0 &      2.84 &    --2.403 &   \nodata &    122.18 &     58.95 &   \nodata &     27.76 \\
 6411.650 &      26.0 &      3.65 &    --0.734 &    122.49 &    135.09 &     97.80 &    131.75 &     68.20 \\
 6469.190 &      26.0 &      4.84 &    --0.770 &   \nodata &   \nodata &     18.72 &   \nodata &   \nodata \\
 6574.230 &      26.0 &      0.99 &    --5.004 &     84.07 &    118.54 &     35.42 &     87.02 &   \nodata \\
 6575.020 &      26.0 &      2.59 &    --2.727 &    100.74 &    118.20 &     55.46 &    103.43 &     23.43 \\
 6581.210 &      26.0 &      1.50 &    --4.705 &     72.41 &     87.47 &     21.69 &     69.56 &   \nodata \\
 6609.110 &      26.0 &      2.56 &    --2.692 &    102.04 &    118.77 &     60.88 &    103.07 &     29.10 \\
 6648.080 &      26.0 &      1.01 &    --5.918 &     37.05 &     54.92 &   \nodata &     37.88 &   \nodata \\
 6739.520 &      26.0 &      1.56 &    --4.820 &     43.10 &     60.83 &   \nodata &     44.46 &   \nodata \\
 6750.150 &      26.0 &      2.42 &    --2.621 &    110.92 &    128.94 &     78.61 &    109.54 &     40.25 \\
 6786.860 &      26.0 &      4.19 &    --1.850 &     22.52 &     29.14 &   \nodata &     32.32 &   \nodata \\
 6810.260 &      26.0 &      4.60 &    --1.000 &     36.16 &     46.93 &     14.51 &     54.86 &      8.49 \\
 6971.930 &      26.0 &      3.02 &    --3.390 &     20.95 &     30.29 &   \nodata &     28.72 &   \nodata \\
 7112.170 &      26.0 &      2.99 &    --3.044 &     45.44 &     59.25 &     13.34 &     52.97 &   \nodata \\
 7189.150 &      26.0 &      3.07 &    --2.796 &     57.46 &     66.29 &   \nodata &   \nodata &   \nodata \\
 7223.660 &      26.0 &      3.01 &    --2.269 &     87.17 &    114.42 &     47.18 &     90.80 &   \nodata \\
 7401.690 &      26.0 &      4.18 &    --1.660 &     38.86 &     50.50 &     14.73 &     59.70 &   \nodata \\
 7710.360 &      26.0 &      4.22 &    --1.129 &     62.55 &     76.72 &     32.47 &     75.37 &   \nodata \\
 7723.200 &      26.0 &      2.28 &    --3.617 &     82.10 &    100.41 &     36.62 &     91.89 &   \nodata \\
 7941.090 &      26.0 &      3.27 &    --2.331 &     50.25 &   \nodata &     22.41 &     61.73 &   \nodata \\
 5234.620 &      26.1 &      3.22 &    --2.150 &   \nodata &     81.16 &   \nodata &   \nodata &     58.33 \\
 5325.550 &      26.1 &      3.22 &    --3.220 &   \nodata &     32.07 &     43.44 &   \nodata &     11.62 \\
 5414.070 &      26.1 &      3.22 &    --3.750 &   \nodata &   \nodata &     23.56 &     20.98 &      6.85 \\
 5425.260 &      26.1 &      3.20 &    --3.370 &     27.09 &     38.20 &     41.32 &     37.29 &     14.47 \\
 5991.380 &      26.1 &      3.15 &    --3.557 &     21.50 &   \nodata &     28.34 &     25.80 &      7.66 \\
 6084.110 &      26.1 &      3.20 &    --3.808 &     11.81 &     15.98 &     20.00 &     18.81 &   \nodata \\
 6149.260 &      26.1 &      3.89 &    --2.724 &     21.75 &     25.19 &     30.83 &     26.28 &     11.80 \\
 6247.560 &      26.1 &      3.89 &    --2.329 &     31.15 &     36.73 &     50.16 &     40.30 &     21.38 \\
 6369.460 &      26.1 &      2.89 &    --4.250 &     13.49 &     16.26 &     18.13 &     16.72 &      5.89 \\
 6416.920 &      26.1 &      3.89 &    --2.740 &     23.09 &     29.20 &     29.18 &     31.92 &   \nodata \\
 6432.680 &      26.1 &      2.89 &    --3.708 &     29.96 &     33.58 &     41.73 &     37.47 &     12.93 \\
 6456.380 &      26.1 &      3.90 &    --2.075 &     40.91 &     47.90 &     61.24 &     49.33 &     30.85 \\
 7224.490 &      26.1 &      3.89 &    --3.243 &   \nodata &   \nodata &     12.70 &     13.24 &   \nodata \\
 7711.720 &      26.1 &      3.90 &    --2.543 &     23.68 &     29.14 &     37.42 &     29.79 &     14.85 \\
 6189.000 &      27.0 &      1.71 &    --2.450 &     51.15 &     77.50 &      9.06 &     58.65 &   \nodata \\
 6455.030 &      27.0 &      3.63 &    --0.250 &     19.14 &     29.82 &   \nodata &     31.42 &   \nodata \\
 6632.450 &      27.0 &      2.28 &    --2.000 &     29.08 &     42.26 &   \nodata &     34.72 &   \nodata \\
 5846.990 &      28.0 &      1.68 &    --3.210 &     60.72 &     77.03 &     17.76 &     62.70 &   \nodata \\
 6086.280 &      28.0 &      4.26 &    --0.515 &     31.84 &     36.07 &     12.42 &     47.85 &   \nodata \\
 6175.370 &      28.0 &      4.09 &    --0.535 &     41.41 &     48.64 &     21.11 &     52.50 &     10.42 \\
